Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-12-01 WSSSPE3/report/wg_main_user_community.tex
adding comment
Start on User Community appendix

@@

Discussion revolved around a few questions: what is the benefit of having a
``community'' for software sustainability, what practices and circumstances lead
to having a community, how can funding help or hinder this process, and perhaps
most importantly, how can best practices be described and distilled into a
document that can help new projects.

>>>>

\katznote{the next little bit needs some work, as Choi points out}

@@

Discussion revolved around a few questions: what is the benefit of having a
``community'' for software sustainability, what practices and circumstances lead
to having and maintaining a community, how can funding help or hinder this
process, and perhaps most importantly, how can best practices be described and
distilled into a document that can help new projects.
